---
title: "PSet7"
author: "Jeffrey Park"
date: "10/13/2021"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

data files converted to CSV files with these commands

echo 'YEAR, MONTH, TIME, CO2 ' >! co2_maunaloa.csv
awk 'NR>53 {print $1 ", " $2 ", " $3 ", " $4}' co2_mm_mlo.txt >> co2_maunaloa.csv



Problem 1


```{r}

mlo_co2 <- read.csv("co2_maunaloa.csv")
names(mlo_co2)
temps <- mlo_co2$DTEMPC
length(temps)
years <- mlo_co2$YEAR
months <- mlo_co2$MONTH
time <- mlo_co2$TIME
co2 <- mlo_co2$CO2


plot(time,co2,col='black',type="l",xlab="",ylab="")
title("Mauna Loa Carbon Dioxide Measurements",xlab="year",ylab="°Parts Per Million")

```

Problem 1a --  fit to Mauna Loa CO2 in decades

```{r}
# pre-define arrays for regression parameters of seven data segments \nuline
ann1 <- 1:7
ann1_err <- 1:7
ann2 <- 1:7
ann2_err <- 1:7
yr <- 1:7


plot(yr,ann1,col='black',xlab="Year",ylab="Annual Cycle Amplitude (ppm CO2)",ylim=range(ann1+ann1_err,ann1-ann1_err))

plot(yr,ann2,col='black',xlab="Year",ylab="SemiAnnual Cycle Amplitude (ppm CO2)",ylim=range(ann2+ann2_err,ann2-ann2_err))



```
Problem 1b --  same plot for the annual cycle phase
```{r}
# pre-define arrays for regression parameters of seven data segments \nuline
ann1_phase <- 1:7
ann1_pherr <- 1:7
ann2_phase <- 1:7
ann2_pherr <- 1:7
yr <- 1:7
pi2 <- 2.0*pi
pi4 <- 4.0*pi

plot(yr,ann1_phase,col='black',xlab="Year",ylab="Annual Cycle Phase (degrees)",ylim=range(ann1_phase+ann1_pherr,ann1_phase-ann1_pherr))

plot(yr,ann2_phase,col='black',xlab="Year",ylab="SemiAnnual Cycle Phase (degrees)",ylim=range(ann2_phase+ann2_pherr,ann2_phase-ann2_pherr))

```
Problem 1c -- plots for time evolution of semi-annual amplitude and phase -

```{r}

```

Problem 2a -- fit log(data) with a two-parameter model

```{r}

plot(time,log(co2))

```
problem 2b -- log everything back and note predicted values in 1958 and 2021
```{r}

exp_pred <- exp(pred_logco2)

print(paste("Predictions for March 1958: ",exp_pred[1],"ppm and August 2021: ",exp_pred[npts]))
print(paste("Actual Values for March 1958: ",co2[1],"ppm and August 2021: ",co2[npts]))
```
Problem 2c -- nonlinear least squares for 3-parameter exponential CO2 model -- test starting values of model parameters
```{r}
# nonlinear fit of log(co2) \nuline
# the nls function in R asks for initial values for the regression parameters \nuline
# which are identified by the start parameter \nuline
names(lm_logco2)

astart <- 
bstart <- 
cstart <- 

time0 <- time-1788

```
Problem 2c -- nonlinear least squares for 3-parameter exponential CO2 model 

```{r}

print(paste(astart,bstart,cstart))

summary(nlm_co2)

```
problem 3a -- Singular value decomposition of the G-matrix, data representers referenced to the midpoint of the time series

```{r}

gsvd <- svd(gmatrix,7,7)
plot(ksing,singval)

print(paste("The condition number is ",condno))

```

Problem 3b -- print out the v-matrix singular vectors with largest and smallest singular values

```{r}

print("v-matrix singular vector with largest singular value")

print("v-matrix singular vector with smallest singular value")


```
problem 3c -- Singular value decomposition of the G-matrix, data representers referenced to the Birth of Christ

```{r}

ksing <- 1:7
data_rep <- time/2000.0
data_rep2 <-  data_rep^2

print(paste("The condition number is ",condno))


```
problem 4 -- bootstrap

```{r}

library(boot)
# define a function to obtain R-Squared from the data
model <- function(formula,data,indices){
  d <- data[indices,]
  fit <- lm(formula,data=d)
  return(coef(fit))
}

co2matrix <- data.frame(data=co2,g1=constant,g2=data_representer,g3=data_representer2,g4=ann_c,g5=ann_s,g6=ann2_c,g7=ann2_s)

# bootstrapping with 1000 replications 
results <- boot(data=co2matrix, statistic=model, 
   R=1000, formula=data~g2+g3+g4+g5+g6+g7)

results
plot(results)

results$t0

```

