---
title: "PSet5"
author: "Jeffrey Park"
date: "9/29/2021"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

data files converted to CSV files with these commands

echo 'YEAR, MONTH, DTEMPC' >! Hadcrut_GlobalAverage.csv
sed 's[/[ [' HadCRUT.4.6.0.0.monthly_ns_avg.txt | awk '{print $1 ", " $2 ", " $3}' >> Hadcrut_GlobalAverage.csv

echo 'YEAR, MONTH, DTEMPC' >! Hadcrut_NHAverage.csv
sed 's[/[ [' HadCRUT.4.6.0.0.monthly_nh.txt | awk '{print $1 ", " $2 ", " $3}' >> Hadcrut_NHAverage.csv

echo 'YEAR, MONTH, DTEMPC' >! Hadcrut_SHAverage.csv
sed 's[/[ [' HadCRUT.4.6.0.0.monthly_sh.txt | awk '{print $1 ", " $2 ", " $3}' >> Hadcrut_SHAverage.csv


Problem 1


```{r}

had_ns_avg <- read.csv("Hadcrut_GlobalAverage.csv")
names(had_ns_avg)
temps <- had_ns_avg$DTEMPC
length(temps)
years <- had_ns_avg$YEAR
months <- had_ns_avg$MONTH

time <- years + (months-0.5)/12.0
time[1:24]

had_sh_avg <- read.csv("Hadcrut_SHAverage.csv")
had_nh_avg <- read.csv("Hadcrut_NHAverage.csv")
temps_sh <- had_sh_avg$DTEMPC
temps_nh <- had_nh_avg$DTEMPC
length(temps_sh)
length(temps_nh)

 
```
Problem 1
plot the data

```{r}


title("Hadley Center Global Average Temperature Anomalies",xlab="year",ylab="°C anomaly referenced to 1961-1990 average")


title("Hadley Center Northern Hemisphere Temperature Anomalies",xlab="year",ylab="°C anomaly referenced to 1961-1990 average")


title("Hadley Center Southern Hemisphere Temperature Anomalies",xlab="year",ylab="°C anomaly referenced to 1961-1990 average")


```
Problem 1a -- t-test on the first and last decades of the 20th century

```{r}

print(paste("mean of 1900s is ",mean1900s," degrees C, with standard deviation ",sdm1900s))
print(paste("mean of 1990s is ",mean1990s," degrees C, with standard deviation ",sdm1990s))

print(testt)

```


Problem 1b -- two-way T-tests of decadal sample means
```{r}


print(testt)
print(testt$statistic)
print(testt$conf.int)

```
Problem 1c -- t.tests of sample means of successive decades
```{r}

decade1_t <- 1:16
decade1_logp <- 1:16
decade2_t <- 1:16
decade2_logp <- 1:16
dtime <- seq(1860,2010,by=10)
dtime

title("Decadal comparisons: Global Average Temperature Anomalies")


```

Problem 1d -- t.tests of sample means of successive decades: Northern Hemisphere
```{r}


par(mfrow=c(2,2))

title("Decadal comparisons: Northern Hemisphere Anomalies")

```
Problem 1d -- t.tests of sample means of successive decades: Southern Hemisphere
```{r}

title("Decadal comparisons: Southern Hemisphere Anomalies")


```
Problem 2a -- Plot some F variance ratio distributions

```{r}

fvarrat <- seq(0.1,10.0,by=0.01)

title(" 2 & 8 (red), 10 & 20 (green) and 17 & 2000 (blue) dof",ylab="F-distribution PDF")

title(" 2 & 8 (red), 10 & 20 (green) and 17 & 2000 (blue) dof",ylab="LOG F-distribution PDF")

```
Problem 2b -- ANOVA with global temperature anomalies


```{r}

decade_means <- 1:17
decade_vars <- 1:17
totpts <- 17*120

print(paste("ANOVA probability of nonrandomness is ",anova_prob,"  p-value: ",pval))

```

Problem 2c -- slice the temp anomalies by month


```{r}

totpts <- 120*12
monthly_means <- 1:12
monthly_vars <- 1:12

print(paste("stdev of within is ",st_within,"  stdev of among is ",st_among))
print(paste("F variance ratio is ",frat))


print(paste("ANOVA probability of nonrandomness is ",anova_prob,"  p-value: ",pval))

```
Problem 3a -- the correlation of hemispheric temperature anomalies


```{r}

rcorr <- 1:17
nn <- 120



```

Problem 3bc -- the correlation of hemispheric temperature anomalies


```{r}


plot(dtime,pvals)


```

  problem 3d -- compute the correlation between the sequences of decadal means 
  for the Northern and Southern Hemispheres
  
```{r}

dmeans_nh <- 1:17
dmeans_sh <- 1:17

print(paste("Correlation probability of nonrandomness is ",rprobs,"  p-value: ",pval))

```