---
title: "Test RStudio command file"
output:
  word_document: default
  html_document: default
---
We pause here before we get to PS 1, Problem 1 and plot some numbers associated with the coin-flip problem

```{r}

h <- 0.5
h
t <- 1.0 - h
t

0.65*0.34

a <- exp(-1)
a
a*0.5
a*h

```

We verify the central identity of the binomial distribution, namely, that the probability of all the cases, taken together is unity, even if we repeat the experiment N times

```{r}

h + t

(h+t)*(h+t)

h^2 + 2*h*t + t^2

(h+t)^4

h^2


```
a) if a coin is flipped three times, what is the probability of two heads and one tails?
```{r}

# (h+t)^3 = h^3 + 3*h*h*t + 3*h*t*t + t^3

(h+t)^3

h^3 + 3*h*h*t + 3*h*t*t + t^3

3*h*h*t

```

b) if a coin is flipped three times, what is the probability of at least two heads?
```{r}

h^3 + 3*h*h*t

```
c) if a coin is flipped 8 times, what is the probability of at least 6 tails?

(h+t)^8 = h^8 + 8*h^7*t + 28*h^6*t^2 + . . . + t^8

```{r}

(h+t)^8
h^8 + 8*h^7*t + 28*h^6*t^2

```
d) if you bet a dollar on every coin flip, what is the probability that you have won at least $4 after eight flips? Does this probability change if you vary your choices of heads or tails for each flip?

```{r}
# word problem -- winning a dollar means that you have one more heads than tails
# winning 2 dollars means that you won two more heads than tails, etc
# to win at least $4 in 8 throws of a die, the heads must occur 6,7, or 8 times.
# so the probablilty is the same as in part (c)

h^8 + 8*h^7*t + 28*h^6*t^2


```
e) Suppose you have combined a large number of card decks (hearts, spades, clubs, diamonds) so that drawing a few cards from the deck does not change the probabilities of drawing a card significantly. (If you draw cards from a single deck, the probability of drawing a King drops by $\sim$25\% after you draw any one King.  We dont want to worry about that effect here.)  If you draw four cards from such a large deck, what is the probability that two or more of the cards will be hearts?

probability of drawing a heart = 1/4 = 0.25

(p+q)^4 = p^4 + 4*p^3*q + 6*p^2*q^2 + 4*p*q^3 + q^4

```{r}
p <- 0.25

q <- 1.0-p

(p+q)^4
p^4 + 4*p^3*q + 6*p^2*q^2 + 4*p*q^3 + q^4

p^4
4*p^3*q
6*p^2*q^2

prob <- p^4 + 4*p^3*q + 6*p^2*q^2

prob

```
f)  If you draw four cards from such a large deck, what is the probability that two or more of the cards will be Jacks?
```{r}
p <- 1.0/13.0

q <- 1.0-p

(p+q)^4
p^4 + 4*p^3*q + 6*p^2*q^2 + 4*p*q^3 + q^4

p^4
4*p^3*q
6*p^2*q^2

prob <- p^4 + 4*p^3*q + 6*p^2*q^2

prob

```
g) if you draw four cards from a single 52-card deck of cards, what is the probability of drawing two jacks?

Here by drawing a card we change the probability of drawing the next card

suppose we draw jack, jack, not-jack, not-jack

p1 <- 4.0/52.0  : probability of drawing first jack
p2 <- 3.0/51.0  : probability of drawing 2nd jack
p3 <- 48.0/50.0 : probability of drawing first not-jack
p4 <- 47.0/49.0 : probability of drawing 2nd not-jack

prob <- p1*p2*p3*p4

there are fac <- 4!/(2!*2!) distinct ways to draw two jacks and two not-jacks
for each combination, the denominator and numerator will be the same

total probability is fac*prob


```{r}
p1 <- 4.0/52.0  # probability of drawing first jack
p2 <- 3.0/51.0  # probability of drawing 2nd jack
p3 <- 48.0/50.0 # probability of drawing first not-jack
p4 <- 47.0/49.0 # probability of drawing 2nd not-jack

prob <- p1*p2*p3*p4
prob

fac <- factorial(4)/(factorial(2)*factorial(2)) # p1*p2*p3*p4
fac
probtot <- fac*prob
probtot

```

```{r}

```

```{r}

x <- rnorm(n=1000, mean=0, sd=1)
plot(x)

```

plot some more random numbers and plot against the first set

```{r}

y <- rnorm(n=1000, mean=0, sd=1)
plot(x,y)

```

combine some more random numbers and plot against the first set, show correlation

```{r}

z <- (x+y)/2
plot(x,z)

```

compute some means

```{r}

a1 <- mean(x)
a2 <- mean(x^2)
a3 <- mean(y)
a4 <- mean(y^2)
a5 <- mean((x+y)^2)
a6 <- mean(z)
a7 <- mean(z^2)
a8 <- mean((x+z)^2)

print(paste(a1,a2,a3,a4,a5,a6,a7,a8))

```

compute some more random numbers and plot

```{r}

x <- rnorm(n=5000, mean=0, sd=1)
plot(x)
```

compute some more random numbers and plot

```{r}


y <- rnorm(n=5000, mean=0, sd=1)
plot(y)

```

plot random numbers against each other

```{r}

plot(x,y)

```

add some correlation and replot

```{r}

z <- (x+y)/2
plot(x,z)


```

```{r}

mean(x)
mean(x^2)
mean(y)
mean(y^2)
mean(z)
mean(z^2)
mean((x+y)^2)
mean((x+z)^2)
b1 <- mean(x)
b2 <- mean(x^2)
b3 <- mean(y)
b4 <- mean(y^2)
b5 <- mean((x+y)^2)
b6 <- mean(z)
b7 <- mean(z^2)
b8 <- mean((x+z)^2)


print(paste(a1,a2,a3,a4,a5,a6,a7,a8))

print(paste(b1,b2,b3,b4,b5,b6,b7,b8))

```


```{r}
xx <- replicate(100,0)
xx2 <- replicate(100,0)
yy <- replicate(100,0)
yy2 <- replicate(100,0)
zz <- replicate(100,0)
zz2 <- replicate(100,0)

for (ii in 1:100){
  x <- rnorm(n=1000, mean=0, sd=1)
  y <- rnorm(n=1000, mean=0, sd=1)
  z <- (x+y)/2
  x2 <- x^2
  y2 <- y^2
  z2 <- z^2

  xx[ii] <- mean(x)
  xx2[ii] <- mean(x2)
  yy[ii] <- mean(y)
  yy2[ii] <- mean(y2)
  zz[ii] <- mean(z)
  zz2[ii] <- mean(z2)
}
hist(x,breaks=21)

hist(xx,breaks=21)
hist(xx2,breaks=21)

hist(yy,breaks=21)
hist(yy2,breaks=21)
hist(zz,breaks=21)
hist(zz2,breaks=21)

```

```{r}

print("xx mean, stdev, vaiance")
mean(xx)
sd(xx)
var(xx)
print("xx^2 mean, stdev, vaiance")
mean(xx2)
sd(xx2)
var(xx2)
print("yy mean, stdev, vaiance")
mean(yy)
sd(yy)
var(yy)
print("yy^2 mean, stdev, vaiance")
mean(yy2)
sd(yy2)
var(yy2)
print("zz mean, stdev, vaiance")
mean(zz)
sd(zz)
var(zz)
print("zz^2 mean, stdev, vaiance")
mean(zz2)
sd(zz2)
var(zz2)

```

```{r}





