---
title: "PSet4"
author: "Jeffrey Park"
date: "9/23/2021"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
Hello Kitty

HADCRUT data file converted to CSV file with these commands

echo 'YEAR, MONTH, DTEMPC' >! Hadcrut_GlobalAverage.csv
sed 's[/[ [' HadCRUT.4.6.0.0.monthly_ns_avg.txt | awk '{print $1 ", " $2 ", " $3}' >> Hadcrut_GlobalAverage.csv


Problem 1


```{r}

had_ns_avg <- read.csv("Hadcrut_GlobalAverage.csv")
names(had_ns_avg)
temps <- had_ns_avg$DTEMPC
length(temps)
years <- had_ns_avg$YEAR
months <- had_ns_avg$MONTH

time <- years + (months-0.5)/12.0
time[1:24]
 
```
Problem 1a
plot the data

```{r}


title("Hadley Center Global Average Temperature Anomalies",xlab="year",ylab="°C anomaly referenced to 1961-1990 average")


```

Problem 1b -- sample mean and sample variance of entire time series
```{r}



```
problem 1c  -- QQ plot
```{r}

title("QQ Plot of Global-Average Temp Anomalies",xlab="Empirical CDF",ylab="Gaussian CDF")


```
problem 1d  -- Beta distribution and the median

```{r}
print(paste("the CDF deviation of the median (\rho) is ",rho))


print(paste("the Beta PDF at the sample median is ",pdf_factor," smaller than at the theoretical median"))


```
Problem 1e -- sample means of decades
```{r}

decade_means <- 1:17
dtime <- seq(1855,2015,by=10)
dtime

title("Hadley Center Global Average Temperature Anomalies")

```
Problem 1f -- compare first and last decades of the 20th century

```{r}


title("first and last decades of 20th century Global-Average Temp Anomalies",xlab="Degrees Celsius",ylab="Empirical and Gaussian CDFs")



```
Problem 2 -- Earthquake distributions

dataset obtained via obspy and Python with

starttime = UTCDateTime("1980-01-01")
#starttime = UTCDateTime("2010-01-01")
endtime = UTCDateTime("2021-01-02")

cat = client1.get_events(starttime=starttime,
      endtime=endtime,minmagnitude=6.0, orderby='magnitude')
original_stdout = sys.stdout # Save a reference to the original standard output
with open('events6.0.txt', 'w') as f:
    sys.stdout = f # Change the standard output to the file we created.
    print(cat.__str__(print_all=True))
    sys.stdout = original_stdout # Reset the standard output to its original value


--> Then manipulated with AWK to form a CSV file to read with R

echo 'YEAR, MONTH, DAY, SLAT, SLON, MAG, MAGTYPE' >! GlobalEarthquakes6.0.csv
sed 's[-[ [g' events6.0.txt | sed 's[T[ [g'  | sed 's[|[ [g'  >! blob
awk 'NR > 1 {print $1 ", " $2 ", " $3 ", " $5 " " $6 ", " $7 ", " $8}' blob >> GlobalEarthquakes6.0.csv

Problem 2cd -- the anti-CDF of earthquake magnitudes

plotting the anti-CDF

let mags be a vector of Richter magnitudes, sorted ascending

nevents <- length(mags)
dstep <- 1.0/nevents
steps <- seq(1.0-dstep/2.0,dstep/2.0,length.out = nevents)
plot(mags,steps,type="l",log="y")

```{r}

gevents <- read.csv("GlobalEarthquakes6.0.csv")
names(gevents)

```
R syntax tricks for extracting values from a data frame

plot(plotframe[,4], plotframe[,5],xlab="PC1",ylab="PC2", col="white")
points(plotframe[plotframe[,2] == name4,4], plotframe[plotframe[,2] == name4,5],col="green",xlab="PC1",ylab="PC2")
points(plotframe[plotframe[,2] == name5,4], plotframe[plotframe[,2] == name5,5],col="red")
points(meanie[1,4:5],meanie[2,4:5],pch=15,col="blue")
title(title3)

# this is a logical array that is TRUE or FALSE, serves as a screen for rows of the 
# dataframe Plotframe that are associate with the string name3 in column 1
loggy <- plotframe[,1] != name3  



Problem 2e -- the frequency of great earthquakes versus Poisson distribution


```{r}

yrs <- 1980:2020
length(yrs)

```

  
