---
title: "PSet8"
author: "Jeffrey Park"
date: "11/11/2021"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

data files written as CSV file gravity_pset8.csv after computation with two secret models

```{r}

Gamma0 <- 6.67408e-11
print(Gamma0)
delzm <- 1000.0
hm <- 10000.0
xim <- 100.0*(-1000:1000)
xi <- xim/1000

w1m <- 0.0
denom <- (w1m-xim)^2 + hm*hm
gi <- 2.0*Gamma0*delzm*hm/denom

plot(xi,gi,'l')

```


#  first model is 


Problem 1a

gj has units xxx

Gram matrix has units xxx

inverse Gram matrix has units xxx

so that the units of alpha are xxx

if we multiply alpha times gj, we have units xxx for drho


Problem 1b
```{r}


Gamma0 <- 6.67408e-11
print(Gamma0)
delzm <- 1000.0
hm <- 10000.0
xim <- 100.0*(-1000:1000)
xi <- xim/1000

plot(xi,gi11,type='l',xlim=c(-60.0,80.0))

lines(xi,gi21,'l')

lines(xi,gi12,'l',col='blue')

lines(xi,gi22,'l',col='blue')

lines(xi,gi13,'l',col='red')

lines(xi,gi23,'l',col='red')

```
Problem 1c

```{r}
# gdata <- data.frame(X = xvm,Dataset1 = gz1,Dataset2 = gz2, StDev = stdgz)

gdata <- read.csv(file="gravity_pset8.csv")
names(gdata)

X <- gdata$X
data1 <- gdata$Dataset1
plot(X,data1)

xx <- 1:N
plot(xx,eval1)
points(xx,eval2,col="blue")
points(xx,eval3,col="red")


print(paste("5-km condition number ",condo1))
print(paste("10-km condition number ",condo2))
print(paste("15-km condition number ",condo3))

```
Problem 1d
```{r}

data1 <- gdata$Dataset1

plot(xi,model1,'l')


plot(xi,model3,"l",col="red")
lines(xi,model2,"l",col="blue")
lines(xi,model1,'l')

```

Problem 1e
```{r}

data2 <- gdata$Dataset2

plot(xi,model1,'l')


plot(xi,model3,"l",col="red")
lines(xi,model2,"l",col="blue")
lines(xi,model1,'l')

```

Problem 2 is all calculus and algebra -- no R programming

Problem 3a
```{r}

hm <- 5000.0

beta_0 <- rep(0.0,N)
xi_0 <- 0.0

plot(xi,model_0,'l')


beta_20 <- rep(0.0,N)
xi_20 <- 20000.0

plot(xi,model_20,'l')


beta_50 <- rep(0.0,N)
xi_50 <- 50000.0

plot(xi,model_50,'l')


```

Problem 3b
```{r}

hm <- 10000.0

beta_0 <- rep(0.0,N)
xi_0 <- 0.0

plot(xi,model_0,'l')


beta_20 <- rep(0.0,N)
xi_20 <- 20000.0

plot(xi,model_20,'l')


beta_50 <- rep(0.0,N)
xi_50 <- 50000.0

plot(xi,model_50,'l')


```


