---
title: "PSet9"
author: "Jeffrey Park"
date: "11/23/2021"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

Problem 1 is all algebra and calculus

Problem 2a
```{r}

time <- 0:99
xdata <- sin(2*pi*time/20)

plot(time,xdata,'l')




```
Problem 2b

```{r}

time <- 0:99
xdata <- sin(2*pi*time/7)


```
Problem 2c
```{r}

xdata <- sin(2*pi*time/20)
xpad <- rep(0.0,1000)
xpad[1:100] <- xdata

```
Problem 3a

# note that both forward and inverse FFTs are unnormalized
# inverse=FALSE --> exp(-i2\pi ft)
# inverse=TRUE --> exp(+i2\pi ft)

```{r}

xdata <- rnorm(1000,mean=0,sd=1)
mean(xdata)
mean(xdata^2)

```

Problem  3b

```{r}
hist(perid,xlim=c(0.0,0.01),breaks=100)


```
Problem 3c

# the amplitude of a deterministic cycle B
# the standard deviation of a zero-mean Gaussian process N(0,A)

```{r}
sig0 <- sin(2*pi*time/20.0)




```

Problem 3d

```{r}
# check out the confidence limits for the chi-squared distribution 
conf <- c(0.9,0.95,0.99,0.999)

```


# deterministic signal of sinusoid 
#
# so to 
```{r}
time <- 0:999


```


Problem 3e

for cycle amplitude B, the periodogram scales as 
and N(0,A) background noise, periodogram scales as 

so if N --> 2N, the threshhold for detecting a cyclic signal 


Problem 3f

```{r}

pgram3 <- rep(0,998)
pgram3 <- (perid[1:998]+perid[2:999]+perid[3:1000])/3



```
Problem 4a

```{r}

mloa <- read.csv("co2_maunaloa.csv")
names(mloa)
ttt <- mloa$TIME
co2 <- mloa$CO2
plot(ttt,co2,type='l')

```
Problem 4b

```{r}

npts <- length(co2_resid)

```
Problem 4c

```{r}

pgram3 <- (pgram[1:(npts-2)]+pgram[2:(npts-1)]+pgram[3:npts])/3.0


```
Problem 4d

```{r}
co2_diff <- rep(0,npts)
co2_diff[2:npts] <- co2_resid[2:npts] - co2_resid[1:(npts-1)]
title(main="Mauna Loa Carbon Dioxide (ppm) first difference")

```
Problem 4e

```{r}
co2pad <- rep(0,6000)
co2pad[0:npts] <- co2_diff
dfpad <- 12.0/6000.0
fpad <- dfpad*(0:5999)

npad <- 6000


```

