---
title: "PSet6"
author: "Jeffrey Park"
date: "9/30/2021"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

data files converted to CSV files with these commands

echo 'YEAR, MONTH, TIME, CO2 ' >! co2_maunaloa.csv
awk 'NR>53 {print $1 ", " $2 ", " $3 ", " $4}' co2_mm_mlo.txt >> co2_maunaloa.csv



Problem 1


```{r}

mlo_co2 <- read.csv("co2_maunaloa.csv")
names(mlo_co2)
temps <- mlo_co2$DTEMPC
length(temps)
years <- mlo_co2$YEAR
months <- mlo_co2$MONTH
time <- mlo_co2$TIME
co2 <- mlo_co2$CO2

title("Mauna Loa Carbon Dioxide Measurements",xlab="year",ylab="°Parts Per Million")

```

Problem 1a -- linear trend fit to Mauna Loa CO2

```{r}

```
Problem 1b -- start and finish CO2 predictions


```{r}


```
Problem 1c --  
```{r}

print(paste("The standard deviation of the data misfit to the linear model is ", sd(residual1)," ppm"))

```
problem 1d -- plot co2 data against the linear model
```{r}


title("Mauna Loa CO2 versus linear-ramp model")

```

Problem 1e -- fit the data with a quadratic

```{r}

print(paste("Starting value of quadratic model is ",start," ppm in March 1958, and finish is ",finish," ppm in August 2021"))

print(paste("Starting value of actual data is ",start0," ppm in March 1958, and finish is ",finish0," ppm in August 2021"))



```
problem 1f -- yearly increases of the quadratic model at start and finish of CO2 series

```{r}

print(paste("Starting CO2 increase per year of quadratic model is ",start_ramp," ppm in 1958-1959, and ending CO2 increase per year is ",finish_ramp," ppm in 2020-2021"))

```
problem 1g -- standard deviation of the misfit to data

```{r}


print(paste("The standard deviation of the data misfit to the quadratic model is ", sd(residual2)," ppm"))

```

problem 1h -- plot the data against quadratic model
```{r}


title("Mauna Loa CO2 versus quadratic model")

```
problem 1i -- cubic model fit

```{r}

print(paste("Starting value of cubic model is ",start," ppm in March 1958, and finish is ",finish," ppm in August 2021"))

print(paste("Starting value of actual data is ",start0," ppm in March 1958, and finish is ",finish0," ppm in August 2021"))


print(paste("The standard deviation of the data misfit to the cubic model is ", sd(residual3)," ppm"))


```
Problem 2 -- add the annual cycle to the co2 datafit

```{r}
pi2 <- 2.0*pi
ann_s <- sin(pi2*time)
ann_c <- cos(pi2*time)

```
Problem 2b -- Annual cycle amplitude

```{r}
print(paste("The amplitude of the full annual cycle is ",coef_ann," ppm with standard deviation ",dcoef_ann," ppm"))
```
Problem 2b -- Annual cycle phase

```{r}


print(paste("peak phase at the year fraction ",peakyr,"  month index is ",peakmon))

```
Problem 2c -- plot residuals of datafit without and with the annual-cycle fit

```{r}

print(paste("The st dev of the data misfit to the quadratic model plus annual cycle is ", sd(residual21)," ppm"))

title("Mauna Loa CO2 series after least squares fits")
```
problem 2d -- fitting a bi-annual term

```{r}

pi4 <- 4.0*pi
ann2_s <- sin(pi4*time)
ann2_c <- cos(pi4*time)


```

```{r}

print(paste("The amplitude of the semi-annual cycle is ",coef2_ann," ppm with standard deviation ",dcoef2_ann," ppm"))

title("Mauna Loa CO2 series annual cycles")

```
Problem 2e -- plot residuals of datafit with annual cycle and with the adjusted annual-cycle fit

```{r}
print(paste("The st dev of the data misfit to the quadratic model plus adjusted annual cycle is ", sd(residual22)," ppm"))


title("Mauna Loa CO2 series after least squares fits")
```
